Viscous Transport in Eroding Porous Media

### 2019-08-27 docs/transport/erosion_transport.tex
add a new figure in transport paper
removed a todo

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b1}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b80}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b160}\\
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b240}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
%\includegraphics[width = 0.37 \textwidth]{./figs/vort_50b160}
\caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
bodies with the fixed pressure drop condition. The color is the
vorticity of the fluid. The 6 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we fixed an eroded geometry and computed an accurate solution by using
the Barycentric quadrature rule for all discretization points.  Then,
for multiple values of $\alpha_\iin$ and $\alpha_\out$, we computed the
velocity field with the trapezoid rule for all points that do not
satisfy conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.  We use these values for all
of our numerical simulations.
\todo[inline]{S-H: What kind of accuracy did this give?  This is less
than the value used by Barnett in his single author quadrature paper.
He said that 5 arclength spacings is the right amount to guarantee
machine precision.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is 0.0216\todo[inline]{SH: Fill in this number}.  At this
resolution, this corresponds to a spacing of $3.0814h$ which is much
too small for the trapezoid rule.  By applying the Barycentric
quadrature rule, there is no issue simulating the erosion until all the
bodies have eroded.

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b1}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b80}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b160}\\
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b240}
\includegraphics[width = 0.3 \textwidth]{./figs/vort_50b320}
\includegraphics[width = 0.38 \textwidth]{./figs/vort_50b400}
\caption{\label{fig:Eroding50vort} Erosion of 50 nearly touching
bodies with the fixed pressure drop condition. The color is the
vorticity of the fluid. The 6 snapshots are evenly spaced in time.}
\end{center}
\end{figure}

@@

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we fixed an eroded geometry and computed an accurate solution by using
the Barycentric quadrature rule for all discretization points.  Then,
for multiple values of $\alpha_\iin$ and $\alpha_\out$, we computed the
velocity field with the trapezoid rule for all points that do not
satisfy conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = 4$ and $\alpha_\out = 4$ give sufficient
accuracy to maintain stability while keeping the number of points that
require the expensive Barycentric quadrature rule to a minimum.  We use
these values for all of our numerical simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is $2.16 \times 10^{-2}$.  At this resolution, this
corresponds to a spacing of $3.0814h$ which is too small for the
trapezoid rule to guarantee a sufficiently small quadrature error.  By
applying the Barycentric quadrature rule, there is no issue simulating
the erosion until all the bodies have eroded.
